---
title: |
  Adding Nudge-based Reminders to Monetary Incentives for Promoting Rubella Antibody Testing and Vaccination
thanks: |
  This study is conducted as a part of the Project ``Implementation of EBPM in Japan'' undertaken at the Research Institute of Economy, Trade and Industry (RIETI). In completing this paper, we thank participants of the EBPM Study Group and the Discussion Paper Study Group of RIETI for their insightful comments. Prior to conducting a randomized controlled trial on an online survey, this study was approved by the Institutional Review Board of the Graduate School of Economics, Osaka University [approval number R020114]. Declarations of interest: none. Funding: This research was financially supported by the Ministry of Health, Labour and Welfare, Japan; the Japan Society for the Promotion of Science [grant number 20H05632 (F., Ohtake)]; and Japan Science and Technology Agency [grant number JPMJPR21R4 (S., Sasaki)].
abstract: |
  We study effects of combining financial incentives with nudges to promote rubella antibody testing and vaccination. In FY2019, the Japanese government began providing vouchers for free testing and vaccination to men aged 40--57 years. Vouchers were mailed to 40--46-year-old men in FY2019. While those aged 47--57 received vouchers in FY2020, they could obtain vouchers and receive testing and vaccination in FY2019 through applying. Focusing on this policy distinction, we conduct a late-FY2019 online field experiment with Japanese 40--57-year-old men. We randomly send nudge-based reminder messages recommending antibody testing and vaccination, and track self-reported behavior until the end of FY2019. One nudge-based reminder with an altruistic message on fetal harm through infection from men to pregnant women significantly promotes antibody testing and vaccination among those who have already received vouchers as a financial incentive. For those who must apply for vouchers, nudge-based reminders have no promoting effect.
  \vskip\baselineskip   
  \noindent
  \textit{JEL classification}: D90, I12, I18

  \noindent
  \textit{Keywords}: Rubella; Vaccination; Antibody Test; Text Messages; Reminders; Free Vouchers.
author:
  - Hiroki Kato
  - Shusaku Sasaki
  - Fumio Ohtake
date: "Last updated on `r format(Sys.Date(), '%B %d, %Y')`"
biblio-style: agsm
bibliography: text-message-2020RCT.bib
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: true
    toc: false
    number_sections: true
    citation_package: natbib
---

```{r chunk-option, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  dev = "pdf",
  fig.width = 15,
  fig.height = 8,
  fig.pos = "t"
)
```

```{r define-class}
library(here)
source(here("R/R6_StartAnalysis.r"))

options(
  knitr.table.format = "latex",
  knitr.kable.NA = "",
  modelsummary_stars_note = FALSE,
  modelsummary_factory_default = "latex"
)
```

# Introduction {#intro}

# Background of Rubella Vaccination in Japan {#background}

# Nationwide Online Survey Experiment {#experiment}

```{r setup}
ctrl <- c(
  "age", "married", "education",
  "income", "noinfo_income",
  "exercise_w1", "health_check", "flushot", "norm",
  "handwash", "temp_check", "avoid_out", "avoid_crowd", "wear_mask"
)

setup <- StartAnalysis$new(here("data/2020-online-survey/shape_survey.csv"))
setup$add_control(ctrl)
main <- setup$main()
```

# Results {#results}
## Study Population {#sample}

Our target population consists of men who did not have antibody testing or vaccinations. We exclude respondents who stated in wave 1 that they had already received either antibody testing or vaccination. In wave 2, we asked respondents whether they had already received either testing or vaccination until wave 1. Thus, when estimating the effect on behavior, we exclude respondents who stated in either wave that they had received either antibody testing or vaccination prior to wave 1.

Our aim is to estimate the effect of text messages in situations where men received monetary incentives as vouchers by default and where they had to incur transaction costs to obtain them. To accomplish this, we create a subsample of men aged 40--46 years and another of men aged 47--56 years. Men in the former subsample automatically received the free vouchers (*default incentive* group). Meanwhile, men in the latter subsample received no incentives or required a costly procedure to get it (*opt-in incentive* group). We believe that most men in the opt-in group did not receive free vouchers in FY2019 because $77.5$% of respondents in wave 1 did not know that rubella routine immunization began in FY2019. Thus, in the default incentive group, monetary incentives and text message reminders are more closely combined than in the opt-in incentive group.

## Effect of Text Messages on Intentions {#intention}

This subsection estimates the effect of text messages on intentions. We find that individuals' observable characteristics are balanced across experimental arms in both default incentive and opt-in incentive group (See Table \@ref(tab:balance-int-default) and \@ref(tab:balance-int-optin) in Appendix). Thus, we first report the difference-in-mean test (t-test) for each group.

### Difference-in-mean Test

```{r ttest-int-test, fig.cap = "Effect of Text Messages on Intention for Antibody Testing Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest()
```

We show the proportion of intention for antibody testing in each experimental arm for the default incentive group (Panel A) and the opt-in incentive group (Panel B) in Figure \@ref(fig:ttest-int-test). The results show that, in the default incentive group only, the Altruistic message increases the intention for antibody testing by a statistically significant $14.3$ pp compared to the MHLW (control) message group ($35.1$% in the Altrustic message group versus $20.8$% in the MHLW (control) message group). Because the Altruistic message changes both the age expression and the message content, the effect relative to MHLW (control) can be interpreted as the combined effect of the two changes. However, MHLW (Age), which only changes the age expression, does not increase intention. Thus, the effect of the Altruistic message is attributed to the message content. Compared to MHLW (Age), Altruistic message content increase the intention for antibody testing by $12.2$ pp ($35.1$% in the Altruistic message group versus $22.9$% in the MHLW (Age) message group), which is statistically significant (see Table \@ref(tab:reg-int-woA) in the Appendix).

On the other hand, in the opt-in incentive group, altruistic messages increased intention by $5.3$ pp, which is statistically insignificant ($32.9$% in the Altrustic message group versus $27.6$% in the MHLW (control) message group).[^optin-altruistic-content] The regression analysis presented later suggests that the Altruistic message effects may differ between the two incentive groups.

[^optin-altruistic-content]:  However, even in the opt-in incentive group, the Altruistic message content may increase testing intention. Compared to the MHLW(age) message group, the Altruistic messages increased the intention to take the antibody test by $7.7$ pp ($32.9$% in the Altruistic message group versus $25.2$% in the MHLW (age) message group), which is statistically significant at the 10% level (see Table \@ref(tab:lh-int-woA) in the Appendix).

```{r ttest-int-vacc, fig.cap = "Effect of Text Messages on Intention for Vaccination Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest(outcome_test = FALSE)
```

Figure \@ref(fig:ttest-int-vacc) depicts the proportions of intention for vaccination for the default incentive group (Panel A) and the opt-in incentive group (Panel B). Results show that in the two incentive groups, most text messages, including the Altruistic messages, do not statistically significantly increase vaccination intentions compared to NHLW (control).

In the opt-in incentive group, the Social Comparison message may lower vaccination intention than the MHLW (control) message ($44.6$% in the Social Comparison message group versus $52.8$% in the MHLW (control) message group).  This result is due to the age expression rather than the message content, as social comparison messages hardly lower intention compared to MHLW (age).[^mechanism]

[^mechanism]: Free-riding may explain why the Social Comparison message content does not increase intention. The Social Comparison message emphasizes that ``one in five people do not have antibodies.'' Conversely, four out of five individuals have antibodies. The readers of such a message may have believed that even if they lacked rubella antibodies, the likelihood of infection would be low because 80% of the population possesses them. When eligible men were required to undergo costly procedures to receive free vouchers, this belief may have made vaccination less beneficial.

Note that the intention ratio of vaccination in all experimental arms is higher than that of antibody testing in both incentive groups. This result may be explained by the stimulus of the question eliciting the vaccination intention. We asked respondents to report their willingness to vaccinate if they did not have antibodies. This condition may strongly stimulate the need for vaccination. Thus, when assessed by actual behavior, the results may differ.

### Regression Analysis

Since age determines whether eligible men received the free vouchers automatically in FY2019, the different effect of text messages for two groups is influenced by the presence or absence of monetary incentives, and by the differences of other dimentions (especially, age) between the two groups. This motivates us to estimate a following linear probability model:
\begin{equation}
\begin{split}
Y_{ij} = &\alpha + \sum_j \beta_j \text{Message}_j + \sum_j \gamma_j (\text{Message}_j \times \text{Opt-in}_i) + \delta \text{Opt-in}_i \\
&+ \lambda X'_{ij} + \epsilon_{ij},
\end{split} \label{eq:regression}
\end{equation}
where $\text{Message}_j$ is a treatment dummy (the reference group is MHLW (control) message), $\text{Opt-in}_i$ is a binary variable indicating the opt-in incentive group (47--56 years old), and $X$ is a set of covariates including age. Our parameter of interest is $\beta_j$ and $\gamma_j$. The parameter $\beta_j$ represents a text message effect for the default incentive group. The linear combination of parameters, $\beta_j + \gamma_j$, is a text message effect for the opt-in incentive group. The parameter $\gamma_j$ shows a difference in the message effect between the two groups.

```{r reg-int}
reg <- main$lm()
reg$reg_tab(
  title = "Regressions of Intention",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-int}
reg$lh_tab(
  title = "Text Message Effects for Opt-in Incentive Group Estimated by Regressions",
  notes = "Notes: * $p < 0.1$, ** $p < 0.5$, *** $p < 0.01$. Robust standard errors are in parentheses. Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

The regression analysis also shows that the Altruistic messages increase the intention to take the antibody test only in the default incentive group (Table \@ref(tab:reg-int)). Controlling for covariates, altruism messages increase the intention to take the antibody test by $16.6$ pp in the default incentive group (column (2)). Furthermore, although marginally statistically significant, the effect of this message weakens by $12.1$ pp as the cost of obtaining a free vaccination ticket becomes more expensive. As a result, the effect of the Altruistic message in the opt-in incentive group is $4.5$ pp, which is not statistically significant (column (2) in Table \@ref(tab:lh-int)). Also statistically insignificant or marginal, the effect of other nudge messages changes in a negative direction as the cost of obtaining free vaccination tickets increases.

Table \@ref(tab:reg-int-woA) in the Appendix estimates the effect of modifying the message content, excluding age expression. In the estimation, we exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Controlling for covariates, the Altruistic message content in the default incentive group statistically significantly increased the intention to take the antibody test by $12.8$ pp, which is the main driver of the positive effect of the Altruistic message in the default incentive group. However, the difference in the effect of message content in the two incentive groups is not statistically significant. Therefore, the F-test results suggest that the Altruistic messages may increase the intention to take the antibody test in the opt-in incentive group (Table \@ref(tab:lh-int-woA) in the Appendix).[^convinient]

[^convinient]: An interesting finding is that only in the opt-in incentive group did the content of the Convinient message statistically significantly increase the intention to take the antibody test by about 9 pp. This group may not have a full understanding of the routine immunization campaign. In fact, the Wave 1 survey shows that only about 20% of the opt-in incentive group are aware of routine vaccination.

## Effect of Text Messages on Behavior {#behavior}

This subsection estimates the effect of text messages on behavior. We tested a balance of individual characteristics again because a few respondents dropped out between waves 1 and 2. The results show that the observable characteristics are balanced across experimental arms in both default incentive and opt-in incentive group (see Table \@ref(tab:balance-act-default) and \@ref(tab:balance-act-optin) in the Appendix). Therefore, we first present the difference-in-mean test (t-test).

### Difference-in-mean Test

```{r ttest-act-test, fig.cap = "Effect of Text Messages on Behavior for Antibody Testing Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest(
  outcome_intention = FALSE,
  label_y_pos = 20,
  breaks_by = 5
)
```

We show the uptake rate of antibody testing in each experimental arm for the default incentive group (Panel A) and the opt-in incentive group (Panel B) in Figure \@ref(fig:ttest-act-test). We find that, as in the intention case, the Altruistic message statistically significantly increases the antibody test uptake rate compared to the MHLW (control) message by $7.4$ pp in the default incentive group only ($10.9$% in the Altruistic message group versus $3.5$% in the MHLW (control) message group).

Unlike the intention case, the effect of the Altruistic messages on behavior is not solely due to the content of the message. Compared to MHLW (Age), which only changed the expression of age, the Altruistic message group increases the antibody test uptake rate by $4.2$ pp ($10.9$% in the Altruistic message group versus $6.7$% in the MHLW (Age) message group). However, regression analysis indicates that this increase is not statistically significant (see Table \@ref(tab:reg-act-woA) in the Appendix). Also, although the regression analysis is not statistically significant, modifying the age expression increases the antibody test uptake rate by $3.2$ pp ($6.7$% in the MHLW (Age) message group versus $3.5$% in the MHLW (Control) message group). Thus, the effect of the Altruistic message on behavior is a combination of the addition of a simple age expression and the revision of the message content.

Selfish messages may boost antibody testing uptake in the default incentive group by $5.5$ pp (9% in the Selfish message group versus $3.5$% in the MHLW (control) message group). Moreover, Social Comparison message may also increase antibody testing uptake in the opt-in incentive group ($4.9$% in the Social Comparison message group versus $3.5$% in the MHLW (control) message group). These effects are statistically significant at the 10% level.

```{r ttest-act-vacc, fig.cap = "Effect of Text Messages on Behavior for Vaccination. Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest(
  outcome_intention = FALSE,
  outcome_test = FALSE,
  label_y_pos = 15,
  breaks_by = 5
)
```

Figure \@ref(fig:ttest-act-vacc) shows the vaccination rates in each experimental arm for the default incentive group (Panel A) and the opt-in incentive group (Panel B).[^policy-effect] In the default incentive group, the Altruistic message may increase the vaccination rate by $3.8$ pp ($4.7$% in the Altruistic message group versus $0.9$% in the MHLW (control) message group). In the same group, the Social Comparison message may also increase vaccination rate by 4 pp ($4.9$% in the Social Comparison message group versus $0.9$% in the MHLW (control) message group). These effects are statistically siginificant at 10% level.

[^policy-effect]: Vaccination is a dummy variable that takes the value of 1 if respondents have been tested and vaccinated. Thus, the vaccination rate can be regarded as the proportion of newly acquired antibodies through vaccination. This outcome variable matches MHLW's policy goal.

### Regression Analysis

```{r reg-act}
reg_act <- main$lm(outcome_intention = FALSE)
reg_act$reg_tab(
  title = "Regressions of Behavior",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-act}
reg_act$lh_tab(
  title = "Text Message Effects on Behavior for Opt-in Incentive Group Estimated by Regressions",
  notes = " Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

As in the case of intention, the different effects of text messages for two incentive group is influenced by dimentions including age difference other than the presence or absence free vouchers. Thus, we estimate a linear probability model (\@ref(eq:regression)) and shows results in Table \@ref(tab:reg-act).

Regression analysis also shows that the Altruistic messages increase antibody test uptake only in the default incentive group. Controlling for covariates, the Altruistic messages increase antibody test uptake by a statistically significant $7.3$ pp in the default incentive group (column (2)). Furthermore, although the statistical significance is weak, the effect of this message weakens by $5.7$ pp as the cost of obtaining a free vaccination ticket becomes more expensive. As a result, the effect of the Altruistic message in the opt-in incentive group is $1.6$ pp, which is not statistically significant (column (2) in Table \@ref(tab:lh-act)). A similar trend is observed for the effect on vaccination, but it is weakly statistically significant.

We summarize the results for the other messages. Controlling for covariates, the Selfish message may have increased the antibody test-taking rate in the default incentive group, although the statistical significance is weak (column (2) in Table \@ref(tab:reg-act)). We also find that the Social Comparison message may have increased antibody testing rates in the two incentive groups (See column (2) in Table \@ref(tab:reg-act) and \@ref(tab:lh-act)). However, the effect size is larger in the default incentive group than in the opt-in incentive group (not a statistically significant difference).

As confirmed by the difference-in-means test, the Social Comparison message may increase vaccination rates in the default incentive group (column (4) in Table \@ref(tab:reg-act)). Although weakly statistically significant, the effect of this message weakens by $5.7$ pp as the cost of obtaining vaccination tickets increases. As a result, the Social Comparison message does not increase vaccination rates in the opt-in incentive group (column (4) in Table \@ref(tab:lh-act)). Again, the effect of the Altruistic message follows a similar trend.

## Monetary Value of Text Messages

Altruistic (and possibly Social Comparison) messages encourage men who received free vouchers by default to obtain antibody testing and be vaccinated. In this subsection, we attempt to evaluate the effect of these messages in the default incentive group in terms of monetary value. That is, we seek to determine the extent to which the nudge messages increase the monetary value of the rubella vaccination. In other words, we are looking for an amount of additional subsidy equivalent to the message effects in terms of government subsidies.

We use willingness to pay (WTP) for the rubella vaccine.[^other-studies] Let $WTP_i$ be an individual's willingness to pay and follow a distribution $F$. Then, for a given cost $C$, men will be vaccinated if $WTP_i \ge C$. The vaccination rate is $F_0 = 1-F(C)$. Suppose that our treated message changes WTP by $\beta$. An individual who receives a treated message will be vaccinated if $WTP_i\ge C-\beta$. The vaccination rate of the treated message group is $F_1 = 1-F(C-\beta)$. Thus, the treated message effect is $\tau = F_1-F_0=F(C)-F(C-\beta)$. From the perspective of government subsidies, the amount of subsidy equal to the effect of the nudge message $\tau$ is $\beta$. We want to estimate $\beta$.

[^other-studies]: Several studies calculate the monetary value of text messages. For example,\cite{Bursztyn2019} calculated it using the two relative effects of financial incentives and text message treatment groups. \cite{Moriwaki2020} also surveyed WTP amounts and calculated monetary value. The latter study is similar to our approach.

Once $F$, $C$, and $\tau$ are determined, we obtain $\beta $. To begin, let us discuss the estimation of $F$ (demand function). We elicit the WTP for vaccination in the first wave before participants read messages. If the vaccination costs 5,000 JPY, we ask respondents if they will get it if the local government pays $s_j$. The subsidy amounts are $s_j \in \{0, 1000, 2000, \ldots , 10000\}$. Let $s_i^{\text{min}}$ be the lowest subsidy at which respondents indicate that they would vaccinate. Let $s_i^{\text{max}}$ be the highest subsidy that respondents indicate they would not vaccinate. We can identify the willingness to pay for vaccination within the range $[5000 - s_i^{\text{max}}, 5000 - s_i^{\text{min}})$. Thus, without additional assumptions, the demand curve is step-wise, and we estimate the monetary value of the message effect with bounds.[^bound-assumption] To obtain a point estimate, we assume that the true WTP is uniformly distributed within the range $[5000 - s_i^{\text{max}}, 5000 - s_i^{\text{min}})$. Then, The vaccination demand curve can then be linearly interpolated (see Figure \@ref(fig:demand-function) in Appendix).

[^bound-assumption]: If respondents indicated that they would not vaccinate at all subsidy amounts, then $s_i^{\text{max}} = 10000$. However, we cannot define $s_i^{\text{min}}$ in the data. Therefore, we assume $s_i^{\text{min}} = 11000$. This assumption does not affect the monetary value of the messages.

In the default incentive group, eligible males receive free vaccination at no cost. Therefore, the natural setting is $C=0$. In addition, the message effect $\tau$ is used for the effect on antibody test uptake. The person taking the antibody test wants to get the antibody, i.e. the vaccination, against rubella. However, the effect of the message on vaccination is different from the effect on (true) vaccination intention, because people with a positive antibody test result cannot be vaccinated. Therefore, $\tau$ is not the effect on vaccination, but the effect on antibody testing.

In our framework, $F_0=1-F(0)$, but one potential concern remains. The message effect $\tau$ is estimated by the difference from the MHLW (control) group, and $F(0)$ does not take into account the $3.5$% antibody test uptake rate of the MHLW (control) (see Figure \@ref(fig:ttest-act-test)). Assuming that everyone who did not participate in our survey did not take the antibody test after the survey, the uptake rate of MHLW (control) can be considered as an effect of providing the message in the survey. To account for this explicitly, we use $F_0=(1-F(0))+(F(0)-F(-\alpha))$. The second term is the antibody testing rate of the control group ($3.5$%) under no vaccination cost. The demand function is estimated to be $F_0=0.7$ and $\alpha=394$.

```{r monetary-value}
value <- main$monetary_value()
value$value_table(
  title = "Estimated Monetary Value of Text Messages",
  notes = "We use the effect size of each text messages on antibody testing. Baseline is the sum of the rate of antibody test in the control and the free vaccination rates. The monetary value is the amount per person multiplied by the number of people who received the coupon in 2019 but did not use it until January 2020 ($5.29$ million). We valued it in Japanese Yen and US Dollars (1 USD = 110 JPY). The unit of monetary value per person is 1 JPY and 1 USD, respectively. The unit of total monetary value is 1 billion JPY and 1 million USD, respectively."
)
```

We find $\beta$ holding that $\tau=F(-\alpha)-F(-\beta)$. Table \@ref(tab:monetary-value) shows the estimated message value. The second and third columns show $\tau$ and $F_1=\tau+F_0$, respectively. The fourth column shows $\beta$ in terms of the value of the Japanese yen (in U.S. dollar value, shown in the sixth column). The Altruistic and Social Comparison message, which promotes antibody testing, value about 2,000 JPY (about 18 USD; 40% of assumed vaccination price) and 600 JPY (about $5.5$ USD; 12% of assumed vaccination price), respectively. The total monetary value is the product of the per capita value and the number of people who have not yet used the free vouchers issued in FY2019 ($5.29$ million as of January 2020). In the fifth column, the Altruistic and Social Comparison messages are worth 10 billion JPY (about 98 million USD) and 3 billion JPY (about 28 million USD), respectively.

# Discussion and Conclusions {#conclusion}

\clearpage
# (APPENDIX) Appendix {-}
# Tables and Figures

```{r covariate-list}
setup$summary_control(here("assets/vars_descript.csv"))
```

```{r balance-int-default}
main$balance_control(
  title = "Balance Tests for Default Incentive Groups (Sample for Estimating Effect on Intention)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2–-8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r balance-int-optin}
main$balance_control(
  default_voucher = FALSE,
  title = "Balance Tests for Opt-In Incentive Group (Sample for Estimating Effect on Intention)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2-–8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r reg-int-woA}
reg_woA <- main$lm(exclude_A = TRUE)
reg_woA$reg_tab(
  title = "Massage Content Effects on Intentions Compared to MHLW (Age)",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-int-woA}
reg_woA$lh_tab(
  title = "Message Content Effects for Opt-in Incentive Group Estimated by Regressions",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

```{r balance-act-default}
main$balance_control(
  outcome_intention = FALSE,
  title = "Balance Tests for Default Incentive Group (Sample for Estimating Effect on Behavior)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2–-8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r balance-act-optin}
main$balance_control(
  outcome_intention = FALSE,
  default_voucher = FALSE,
  title = "Balance Tests for Opt-in Incentive Group (Sample for Estimating Effect on Behavior)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2-–8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r reg-act-woA}
reg_act_woA <- main$lm(outcome_intention = FALSE, exclude_A = TRUE)
reg_act_woA$reg_tab(
  title = "Message Content Effects on Behaivor Compared to MHLW (Age)",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-act-woA}
reg_act_woA$lh_tab(
  title = "Message Content Effects for Opt-in Incentive Group Estimated by Regressions",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

```{r demand-function, fig.cap = "Demand Curve of Rubella Vaccination for Default Incentive Group. Notes: Black triangles indicate the baseline vaccination rate $F_0$ and the corresponding WTP."}
value$demand_curve()
```