---
title: |
  Adding Nudge-based Reminders to Monetary Incentives for Promoting Rubella Antibody Testing and Vaccination
thanks: |
  This study is conducted as a part of the Project "Implementation of EBPM in Japan" undertaken at the Research Institute of Economy, Trade and Industry (RIETI). In completing this paper, we thank participants of the EBPM Study Group and the Discussion Paper Study Group of RIETI for their insightful comments. Prior to conducting a randomized controlled trial on an online survey, this study was approved by the Institutional Review Board of the Graduate School of Economics, Osaka University [approval number R020114]. Declarations of interest: none. Funding: This research was financially supported by the Ministry of Health, Labour and Welfare, Japan; the Japan Society for the Promotion of Science [grant number 20H05632 (F., Ohtake)]; and Japan Science and Technology Agency [grant number JPMJPR21R4 (S., Sasaki)].
abstract: |
  We study effects of combining financial incentives with nudges to promote rubella antibody testing and vaccination. In FY2019, the Japanese government began providing vouchers for free testing and vaccination to men aged 40--57 years. Vouchers were mailed to 40--46-year-old men in FY2019. While those aged 47--57 received vouchers in FY2020, they could obtain vouchers and receive testing and vaccination in FY2019 through applying. Focusing on this policy distinction, we conduct a late-FY2019 online field experiment with Japanese 40--57-year-old men. We randomly send nudge-based reminder messages recommending antibody testing and vaccination, and track self-reported behavior until the end of FY2019. One nudge-based reminder with an altruistic message on fetal harm through infection from men to pregnant women significantly promotes antibody testing and vaccination among those who have already received vouchers as a financial incentive. For those who must apply for vouchers, nudge-based reminders have no promoting effect.
  \vskip\baselineskip   
  \noindent
  \textit{JEL classification}: D90, I12, I18

  \noindent
  \textit{Keywords}: Rubella; Vaccination; Antibody Test; Text Messages; Reminders; Free Vouchers.
author:
  - Hiroki Kato
  - Shusaku Sasaki
  - Fumio Ohtake
date: "Last updated on `r format(Sys.Date(), '%B %d, %Y')`"
biblio-style: agsm
bibliography: text-message-2020RCT.bib
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
    keep_tex: true
    toc: false
    number_sections: true
    citation_package: natbib
---

```{r chunk-option, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE,
  dev = "pdf",
  fig.width = 15,
  fig.height = 8,
  fig.pos = "t"
)
```

```{r define-class}
library(here)
source(here("R/R6_StartAnalysis.r"))

options(
  knitr.table.format = "latex",
  knitr.kable.NA = "",
  modelsummary_stars_note = FALSE,
  modelsummary_factory_default = "latex"
)
```

# Introduction {#intro}


Vaccination is an essential countermeasure against infectious diseases, including COVID-19, seasonal influenza, and rubella. Vaccination enables individuals to voluntarily acquire antibodies and immunity. They can thus prevent the onset of infectious diseases and even infection itself.

Vaccination has positive externalities and benefits for the vaccinated individuals, surrounding community, and society. For example, vaccination lowers the risk of developing an infectious disease or becoming severely ill. It also reduces the risk of the health-care delivery system becoming strained. Vaccination with infection-preventive effects, including the rubella vaccine, reduces the risk of infection for the vaccinated and the risk of spreading the infection. Vaccination can contribute to social stability during pandemics and the acquisition of herd immunity via these positive externalities.

However, economic theories suggest that vaccination rates may not reach the socially optimal level due to the positive externalities [@Brito1991a; @Francis1997; @Stiglitz2000]. With the externalities, the marginal individual benefit of vaccination becomes lower than the marginal social benefit, and this feature discourages vaccination by those with selfish motives. Even if people are altruistic and gain utility from the social benefits of their vaccinations reducing the infection probability of others, they still have an incentive to free-ride on others' vaccinations and not receive the vaccines themselves, because the infection probability is lowered by the others' vaccinations. We find empirical studies reporting that others' increased vaccination rates reduce the likelihood of people being vaccinated [@Hershey1994; @Ibuka2014].

To overcome the challenge of vaccine coverage not achieving socially optimal levels, governments have used a variety of interventions, including monetary and non-monetary interventions (nudges in behavioral economics). Many countries subsidize COVID-19 vaccinations, making them free. Some local governments set subsidies above and beyond the amount required to make vaccination free, giving vaccinated people the right to join a lottery, and recent studies have confirmed the effectiveness of these measures [@Barber2022; @Brehm2022]. Nudge-based interventions include recommending a predetermined vaccination date, sending a reminder message, and changing message wording [@Chapman2010; @Sasaki2022; @Yokum2018].[^owner-ship]

[^owner-ship]: In the context of vaccines for seasonal influenza and COVID-19, some studies found that messages stimulating people's ownership, "A vaccine dose is reserved for you," promotes their vaccination uptake [@Dai2021; @Milkman2021].

This study explores the possibility of combining financial incentives with nudges in vaccination and antibody acquisition. Many previous studies estimated or compared these two as independent or substitutive. However, Richard Thaler and Cass Sunstein define nudges as "an aspect of choice architecture that alters people's behaviour in a predictable way without forbidding any options or significantly changing their economic incentives" [@Thaler2009, p.6]. As mentioned, "without significantly altering economic incentives," nudges include devising wordings and expressions for existing financial incentives. They further explain that nudges adjust the salience of financial incentives so that the incentives have the expected effect.[^def-nudge] In other words, nudges and financial incentives are complementary in their original definition.

[^def-nudge]: They mention "iNcentives," "Understand mappings," "Defaults," "Give feedback," "Expect error," and "Structure complex choices" as the six principles of "NUDGES" for creating a good choice architecture. The first principle, "iNcentives," explains the complementary relationship between financial incentives and nudges.

Recently, more studies have examined the two combinations in non-vaccination contexts. For example, @Burtch2018 found that combining a nudge emphasizing social norms with a financial incentive improves the length and quality of online market reviews more than either intervention alone. @Thorndike2016 reported similar results regarding healthy food choices in a hospital cafeteria. Meanwhile, in the study of @Kullgren2014, combining nudges and financial incentives does not increase outdoor exercise among older adults. Furthermore, @Pellerano2017 reported that adding a financial incentive to a social norm nudge undermines the energy-saving effect of the nudge-based intervention alone.[^lab] We can expect relatively large facilitating effects in combining nudges and financial incentives, while in practice, the effects' direction and extent depend on contexts. Before applying the combinations to policies, we must confirm their effects empirically.

[^lab]: Besides field experimental studies, some laboratory experimental studies have also tested the effects of the combination; @Chen2021 show that combining a financial incentive with an informational nudge induces cooperative behaviors in a prisoner's dilemma game among intrinsically motivated individuals.

To the best of our knowledge, no study has focused on the combination of financial incentives and nudges in the context of vaccination. As previously stated, many previous studies have separately estimated the effects of financial incentives [@Banerjee2010; @Barber2022; @Barham2009; @Brehm2022] and nudges [@Dai2021; @Chapman2010; @Milkman2021; @Sasaki2022] as stand-alone measures. Although some studies focused on both, they compared the effects of the two interventions, examined which is larger, and seemed to regard the two as substitutive. For example, @Bronchetti2015 conducted a randomized controlled trial with college students in Pennsylvania and found that a financial incentive increases their seasonal influenza vaccination rate. In this experiment, a peer-related nudge increases vaccine information exposure but does not increase vaccination rates. @Campos-Mercade2021a reported that a €20 financial incentive increases vaccination rates by 4 percentage points (pp) in a Swedish field experiment and emphasized that some nudge-based interventions have little promotional effect.

We add new insights to the literature on the combination of financial incentives and nudges, by focusing on Japan's policy on rubella antibody testing and vaccination and conducting a nationwide online field experiment. We estimate the effect of providing nudge-based messages in each of the situation where people can easily obtain financial incentives and where they must incur additional transaction costs to obtain the incentives. In the former situation, financial incentives and nudges are more closely combined.

In Japan, men born between April 2, 1962, and April 1, 1979 (aged 40--57 years as of 2019) have historically been excluded from routine rubella immunization (see Section \@ref(background) for details). Consequently, men in this age group have lower antibody prevalence than their female counterparts. Therefore, Japan has yet to achieve herd immunity against rubella. Unlike flu and COVID-19 vaccinations, rubella vaccine-induced immunity is long-lasting, and people without antibodies must receive a single vaccination to achieve herd immunity against rubella. The Ministry of Health, Labor, and Welfare (MHLW) then initiated an additional measure for routine rubella vaccination in FY2019 by mailing vouchers covering the costs of the rubella antibody test (approximately 5,000 JPY, which is equal to 45 US dollars) and vaccination (approximately 10,000 JPY) to men aged 40--57 years, to confirm whether they have an antibody and then encourage vaccination for those without it.[^exchange]

[^exchange]: We assume 1 USD = 110 JPY.

Free vouchers were distributed progressively through local governments: vouchers were mailed to men aged 40--46 in FY2019 and those aged 47--57 years in FY2020. Men aged 47--57 years had to apply to their local government to receive the vouchers during FY2019. That is, in FY2019, men aged 40--46 years received the free vouchers as financial incentives by default, whereas men aged 47--57 years had to opt-in to receive the vouchers, incurring transaction costs.

We conducted an online field experiment in February--March 2020 (at the end of FY2019) with men aged 40--57 years living throughout Japan, including the aforementioned two age groups. In this study, we use a randomized controlled trial (RCT) and send reminders with nudge-based messages to encourage the uptake of antibody testing and vaccination. We ascertain their intentions to receive the test and vaccine, and their self-reported behaviors to receive them in a follow-up survey.

By focusing on the sample aged 40--46 years, we can capture the effects of providing additional reminders with nudged messages in one situation where they already obtained the vouchers as financial incentives. Meanwhile, we can capture the effects of providing reminders in another situation where they must incur transaction costs and opt-in to obtain financial incentives with the sample aged 47--57 years. In other words, this study focuses on the combination of nudges and the costs of acquiring financial incentives. The approach of reducing these costs by delivering vouchers to the target population is observed in a variety of policy issues. Therefore, exploring this realistic combination of financial incentives and nudges is important from a policy perspective.

In each of the group who obtain the financial incentive by default and the other group who needs to opt-in, our experiment randomly offers either of a control reminder message with no nudge and six nudge-based reminder messages. The main finding reveals that a reminder with an altruistic message is effective in promoting antibody testing and vaccination behaviors only in the former group. This altruistic message emphasizes the negative impact on newborns caused by infection from the men to pregnant women.

This study contributes to the literature exploring the conditions under which nudges work effectively. Evidence for the effectiveness of nudges has been mixed in recent years; according to a meta-analysis by @DellaVigna2022a, nudges are not large in reality, and their effectiveness depends on various conditions, including topics and channels. This study focuses on the combination of financial incentives and nudges, which have often been treated as mutually substitutive measures, and demonstrates that nudges can be effective when given to a group that has already obtained financial incentives. This result is also consistent with the original definition of the two being complementary.

This research also contributes to acquiring global herd immunity against rubella; according to the World Health Organization, 101 of 194 countries have not yet eliminated rubella, accounting for 52\% [@Zimmerman2022]. Specifically, in the Eastern Mediterranean, South-East Asia, and Western Pacific regions, the proportion of countries that have not yet achieved herd immunity is high. As cross-border traffic increases toward the end of the COVID-19 pandemic, achieving herd immunity against rubella will become increasingly important for the remaining countries. Japan is extremely close to achieving herd immunity. The nudge-based strategy used in such a country to acquire that last mile will be useful for many other countries in the future.

The rest of this paper is structured as follows. Section \@ref(background) provides an overview of rubella in Japan. Section \@ref(experiment) describes the experimental design and Section \@ref(results) presents the results. Finally, Section \@ref(conclusion) discuss results and concludes the paper.

# Background of Rubella Vaccination in Japan {#background}

# Nationwide Online Survey Experiment {#experiment}

In collaboration with MHLW, we commissioned MyVoiceCome Co.~Ltd. to conduct two nationwide online surveys at the end of FY2019. On February 15--17, 2020, we conducted the first survey (wave 1) of 4,200 Japanese men aged 40--59 years living throughout Japan. Wave 1 randomizes seven text messages to test how they affect antibody testing and vaccination intentions.
On  March 17--25, 2020, we surveyed wave 1 respondents again for the second survey (wave 2). We received responses from 3,963 individuals (attrition rate = 5.64\%).\footnote{The seven experimental arms have similar attrition rates. We linearly regress an attrition dummy on treatment group dummies. F-test for joint null hypothesis is statistically insignificant (F-value = $1.434$; p-value = $0.197$).} Wave 2 aims to test how the randomly assigned text messages in wave 1 affect the actual uptake of antibody testing and vaccination.

Online Appendix B contains detailed information about the survey. We obtained prior approval from the IRB of the Graduate School of Economics, Osaka University (approval number: R020114) for conducting the RCT on the online survey.

## Wave 1: Treatments and Outcome Variables on Intention {#wave1}

```{r setup}
ctrl <- c(
  "age", "married", "education",
  "income", "noinfo_income",
  "exercise_w1", "health_check", "flushot", "norm",
  "handwash", "temp_check", "avoid_out", "avoid_crowd", "wear_mask"
)

setup <- StartAnalysis$new(here("data/2020-online-survey/shape_survey.csv"))
setup$add_control(ctrl)
main <- setup$main()
```

```{r message-list}
setup$summary_assign(here("assets/nudge_descript.csv"))
```

We randomly sent one of the text messages in Table \@ref(tab:message-list). The *MHLW (Control)* message is the control. Using this message, MHLW promotes antibody testing and rubella vaccination against rubella on its website (business-as-usual control). We developed six additional text messages based on the MHLW (Control) message to explore what elements to use and how to emphasize them. Recent behavioral science research has increasingly investigated the efficacy of multiple candidate messages [e.g., @Dai2021; @Milkman2021], similar to this study.

The six treated text messages alter the MHLW (Control) message to (1) a simple age expression and (2) behavioral economics content. In addition to the precise target age for the additional rubella measures, the *MHLW (Age)* message includes the simple phrase "men in their 40s and 50s," which helps the reader understand if they are eligible for vaccination and pay attention to the message. The MHLW (Age) message only changed the age expression; the message's content is identical to the control. The other five messages both add simplified age expressions and change message content based on behavioral economics.

The *Altruistic* message describes how one's infection can harm others, particularly pregnant women and their children. As previously stated, vaccination has positive externalities. In the case of rubella, having antibodies through vaccination prevents infection in pregnant women, thus protecting their children. The Altruistic message is the inverse of this positive externality, emphasizing the negative externality of not being vaccinated. This message is intended to help altruistic readers imagine the negative externalities caused by the infection and change their behavior.[^def-altruistic]

[^def-altruistic]: We define an altruistic person as someone who considers social benefits, including externalities.

The *Selfish* message and *Social Comparison* message aim to change behavior by increasing the importance of having rubella antibodies. The Selfish one describes in detail the damage caused by the infection to the individual, making it easier for the reader to imagine it. Meanwhile, the Social Comparison informs the reader that antibody prevalence is low and reminds them that they are susceptible to infection. This message can help people avoid underestimating the likelihood of infection and undervaluing vaccination.

The *Deadline* message and *Convenient* message describe the routine vaccination system. Deadline emphasizes that the FY2019 vouchers are valid until the end of March. This message aims to prevent people from postponing antibody testing and vaccination due to the present bias, which is one of behavioral economics' key findings. Meanwhile, Convenient states that some people can get antibody testing as part of a regular health examination and emphasizes its convenience. This message aims to reduce the subjective cost of antibody testing.

We employed stratified randomization. The survey firm divided respondents into four age groups (40--44, 45--49, 50--54, and 55--59) and equally assigned messages within each stratum. The sample size for each group is 1,050, with 150 for one experimental arm within each group. Thus, the sample size for one experimental group is 600.[^age]

[^age]: The ages shown in Table \@ref(tab:message-list) are as of April 2019, calculated using the year and month of respondents' birth. Men aged 40--56 years as of April 2019 are eligible for the MHLW's additional measures. Those aged 40--46 years automatically receive coupons for the first year. We assume that those born in April have not yet reached their birthday. Also, some men aged 39 years as of April 2019 were 40 years old at the time of the survey.

In wave 1, after viewing a randomly assigned message, participants expressed their intention to get antibody testing and vaccinated on a 5-point Likert scale (5 = definitely yes; 1 = absolutely no). The question of willingness to take antibody testing is, "Are you willing to take an antibody test for rubella now?" Meanwhile, the intention to get vaccinated question asks, "If the antibody testing reveals that you have no antibodies, are you willing to get vaccinated?" We create a binary variable taking the value of 1 if the participant responds 4 or 5 for each question and use it as the outcome variable for intentions.

## Wave 2: Outcome Variables on Behavior {#wave2}

Wave 2 investigates actual antibody testing and vaccination behavior since wave 1. We present exact questions and choices about antibody testing and vaccination in Online Appendix B. We create a binary variable taking 1 if the respondent has taken antibody testing since the end of wave 1.

To receive rubella vaccination through routine immunization, eligible men must first undergo antibody testing. However, they may have been vaccinated against rubella at their own expense without having their antibodies tested. To eliminate this possibility, we create a binary variable taking 1 if respondents have been tested and vaccinated since the end of wave 1.Then, we use it as the outcome variable on vaccination coverage.

Although self-reported behavioral measures may be subject to the experimenter demand effect and social desirability bias, the design and analysis of the current study addresses these biases in the following two ways. First, because this study is a randomized controlled trial and if these biases exist to the same extent in each group, they are not fatal to the identification of treatment effects. Second, even if these biases are heterogeneous across groups, our analysis directly controls for respondents' psychological factors related to these biases (feeling pleasure from acting for others, accepting bad behavior in anonymous conditions) and then estimates treatment effects.

# Results {#results}
## Study Population {#sample}

Our target population consists of men who did not have antibody testing or vaccinations. We exclude respondents who stated in wave 1 that they had already received either antibody testing or vaccination. In wave 2, we asked respondents whether they had already received either testing or vaccination until wave 1. Thus, when estimating the effect on behavior, we exclude respondents who stated in either wave that they had received either antibody testing or vaccination prior to wave 1.

Our aim is to estimate the effect of text messages in situations where men received monetary incentives as vouchers by default and where they had to incur transaction costs to obtain them. To accomplish this, we create a subsample of men aged 40--46 years and another of men aged 47--56 years. Men in the former subsample automatically received the free vouchers (*default incentive* group). Meanwhile, men in the latter subsample received no incentives or required a costly procedure to get it (*opt-in incentive* group). We believe that most men in the opt-in group did not receive free vouchers in FY2019 because $77.5$% of respondents in wave 1 did not know that rubella routine immunization began in FY2019. Thus, in the default incentive group, monetary incentives and text message reminders are more closely combined than in the opt-in incentive group.

## Effect of Text Messages on Intentions {#intention}

This subsection estimates the effect of text messages on intentions. We find that individuals' observable characteristics are balanced across experimental arms in both default incentive and opt-in incentive group (See Table \@ref(tab:balance-int-default) and \@ref(tab:balance-int-optin) in Appendix). Thus, we first report the difference-in-mean test (t-test) for each group.

### Difference-in-mean Test

```{r ttest-int-test, fig.cap = "Effect of Text Messages on Intention for Antibody Testing Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest()
```

We show the proportion of intention for antibody testing in each experimental arm for the default incentive group (Panel A) and the opt-in incentive group (Panel B) in Figure \@ref(fig:ttest-int-test). The results show that, in the default incentive group only, the Altruistic message increases the intention for antibody testing by a statistically significant $14.3$ pp compared to the MHLW (control) message group ($35.1$% in the Altrustic message group versus $20.8$% in the MHLW (control) message group). Because the Altruistic message changes both the age expression and the message content, the effect relative to MHLW (control) can be interpreted as the combined effect of the two changes. However, MHLW (Age), which only changes the age expression, does not increase intention. Thus, the effect of the Altruistic message is attributed to the message content. Compared to MHLW (Age), Altruistic message content increase the intention for antibody testing by $12.2$ pp ($35.1$% in the Altruistic message group versus $22.9$% in the MHLW (Age) message group), which is statistically significant (see Table \@ref(tab:reg-int-woA) in the Appendix).

On the other hand, in the opt-in incentive group, altruistic messages increased intention by $5.3$ pp, which is statistically insignificant ($32.9$% in the Altrustic message group versus $27.6$% in the MHLW (control) message group).[^optin-altruistic-content] The regression analysis presented later suggests that the Altruistic message effects may differ between the two incentive groups.

[^optin-altruistic-content]:  However, even in the opt-in incentive group, the Altruistic message content may increase testing intention. Compared to the MHLW(age) message group, the Altruistic messages increased the intention to take the antibody test by $7.7$ pp ($32.9$% in the Altruistic message group versus $25.2$% in the MHLW (age) message group), which is statistically significant at the 10% level (see Table \@ref(tab:lh-int-woA) in the Appendix).

```{r ttest-int-vacc, fig.cap = "Effect of Text Messages on Intention for Vaccination Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest(outcome_test = FALSE)
```

Figure \@ref(fig:ttest-int-vacc) depicts the proportions of intention for vaccination for the default incentive group (Panel A) and the opt-in incentive group (Panel B). Results show that in the two incentive groups, most text messages, including the Altruistic messages, do not statistically significantly increase vaccination intentions compared to NHLW (control).

In the opt-in incentive group, the Social Comparison message may lower vaccination intention than the MHLW (control) message ($44.6$% in the Social Comparison message group versus $52.8$% in the MHLW (control) message group).  This result is due to the age expression rather than the message content, as social comparison messages hardly lower intention compared to MHLW (age).[^mechanism]

[^mechanism]: Free-riding may explain why the Social Comparison message content does not increase intention. The Social Comparison message emphasizes that "one in five people do not have antibodies." Conversely, four out of five individuals have antibodies. The readers of such a message may have believed that even if they lacked rubella antibodies, the likelihood of infection would be low because 80% of the population possesses them. When eligible men were required to undergo costly procedures to receive free vouchers, this belief may have made vaccination less beneficial.

Note that the intention ratio of vaccination in all experimental arms is higher than that of antibody testing in both incentive groups. This result may be explained by the stimulus of the question eliciting the vaccination intention. We asked respondents to report their willingness to vaccinate if they did not have antibodies. This condition may strongly stimulate the need for vaccination. Thus, when assessed by actual behavior, the results may differ.

### Regression Analysis

Since age determines whether eligible men received the free vouchers automatically in FY2019, the different effect of text messages for two groups is influenced by the presence or absence of monetary incentives, and by the differences of other dimentions (especially, age) between the two groups. This motivates us to estimate a following linear probability model:
\begin{equation}
\begin{split}
Y_{ij} = &\alpha + \sum_j \beta_j \text{Message}_j + \sum_j \gamma_j (\text{Message}_j \times \text{Opt-in}_i) + \delta \text{Opt-in}_i \\
&+ \lambda X'_{ij} + \epsilon_{ij},
\end{split} \label{eq:regression}
\end{equation}
where $\text{Message}_j$ is a treatment dummy (the reference group is MHLW (control) message), $\text{Opt-in}_i$ is a binary variable indicating the opt-in incentive group (47--56 years old), and $X$ is a set of covariates including age. Our parameter of interest is $\beta_j$ and $\gamma_j$. The parameter $\beta_j$ represents a text message effect for the default incentive group. The linear combination of parameters, $\beta_j + \gamma_j$, is a text message effect for the opt-in incentive group. The parameter $\gamma_j$ shows a difference in the message effect between the two groups.

```{r reg-int}
reg <- main$lm()
reg$reg_tab(
  title = "Regressions of Intention",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-int}
reg$lh_tab(
  title = "Text Message Effects for Opt-in Incentive Group Estimated by Regressions",
  notes = "Notes: * $p < 0.1$, ** $p < 0.5$, *** $p < 0.01$. Robust standard errors are in parentheses. Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

The regression analysis also shows that the Altruistic messages increase the intention to take the antibody test only in the default incentive group (Table \@ref(tab:reg-int)). Controlling for covariates, altruism messages increase the intention to take the antibody test by $16.6$ pp in the default incentive group (column (2)). Furthermore, although marginally statistically significant, the effect of this message weakens by $12.1$ pp as the cost of obtaining a free vaccination ticket becomes more expensive. As a result, the effect of the Altruistic message in the opt-in incentive group is $4.5$ pp, which is not statistically significant (column (2) in Table \@ref(tab:lh-int)). Also statistically insignificant or marginal, the effect of other nudge messages changes in a negative direction as the cost of obtaining free vaccination tickets increases.

Table \@ref(tab:reg-int-woA) in the Appendix estimates the effect of modifying the message content, excluding age expression. In the estimation, we exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Controlling for covariates, the Altruistic message content in the default incentive group statistically significantly increased the intention to take the antibody test by $12.8$ pp, which is the main driver of the positive effect of the Altruistic message in the default incentive group. However, the difference in the effect of message content in the two incentive groups is not statistically significant. Therefore, the F-test results suggest that the Altruistic messages may increase the intention to take the antibody test in the opt-in incentive group (Table \@ref(tab:lh-int-woA) in the Appendix).[^convinient]

[^convinient]: An interesting finding is that only in the opt-in incentive group did the content of the Convinient message statistically significantly increase the intention to take the antibody test by about 9 pp. This group may not have a full understanding of the routine immunization campaign. In fact, the Wave 1 survey shows that only about 20% of the opt-in incentive group are aware of routine vaccination.

## Effect of Text Messages on Behavior {#behavior}

This subsection estimates the effect of text messages on behavior. We tested a balance of individual characteristics again because a few respondents dropped out between waves 1 and 2. The results show that the observable characteristics are balanced across experimental arms in both default incentive and opt-in incentive group (see Table \@ref(tab:balance-act-default) and \@ref(tab:balance-act-optin) in the Appendix). Therefore, we first present the difference-in-mean test (t-test).

### Difference-in-mean Test

```{r ttest-act-test, fig.cap = "Effect of Text Messages on Behavior for Antibody Testing Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest(
  outcome_intention = FALSE,
  label_y_pos = 20,
  breaks_by = 5
)
```

We show the uptake rate of antibody testing in each experimental arm for the default incentive group (Panel A) and the opt-in incentive group (Panel B) in Figure \@ref(fig:ttest-act-test). We find that, as in the intention case, the Altruistic message statistically significantly increases the antibody test uptake rate compared to the MHLW (control) message by $7.4$ pp in the default incentive group only ($10.9$% in the Altruistic message group versus $3.5$% in the MHLW (control) message group).

Unlike the intention case, the effect of the Altruistic messages on behavior is not solely due to the content of the message. Compared to MHLW (Age), which only changed the expression of age, the Altruistic message group increases the antibody test uptake rate by $4.2$ pp ($10.9$% in the Altruistic message group versus $6.7$% in the MHLW (Age) message group). However, regression analysis indicates that this increase is not statistically significant (see Table \@ref(tab:reg-act-woA) in the Appendix). Also, although the regression analysis is not statistically significant, modifying the age expression increases the antibody test uptake rate by $3.2$ pp ($6.7$% in the MHLW (Age) message group versus $3.5$% in the MHLW (Control) message group). Thus, the effect of the Altruistic message on behavior is a combination of the addition of a simple age expression and the revision of the message content.

Selfish messages may boost antibody testing uptake in the default incentive group by $5.5$ pp (9% in the Selfish message group versus $3.5$% in the MHLW (control) message group). Moreover, Social Comparison message may also increase antibody testing uptake in the opt-in incentive group ($4.9$% in the Social Comparison message group versus $3.5$% in the MHLW (control) message group). These effects are statistically significant at the 10% level.

```{r ttest-act-vacc, fig.cap = "Effect of Text Messages on Behavior for Vaccination. Notes: Numbers in the figure indicate the proportion of each experimental arm. Error bars indicate the standard error of the mean. Asterisks are p-values of t-tests for the difference-in-mean: * $p < 0.1$, ** $p < 0.05$, *** $p < 0.01$."}

main$ttest(
  outcome_intention = FALSE,
  outcome_test = FALSE,
  label_y_pos = 15,
  breaks_by = 5
)
```

Figure \@ref(fig:ttest-act-vacc) shows the vaccination rates in each experimental arm for the default incentive group (Panel A) and the opt-in incentive group (Panel B).[^policy-effect] In the default incentive group, the Altruistic message may increase the vaccination rate by $3.8$ pp ($4.7$% in the Altruistic message group versus $0.9$% in the MHLW (control) message group). In the same group, the Social Comparison message may also increase vaccination rate by 4 pp ($4.9$% in the Social Comparison message group versus $0.9$% in the MHLW (control) message group). These effects are statistically siginificant at 10% level.

[^policy-effect]: Vaccination is a dummy variable that takes the value of 1 if respondents have been tested and vaccinated. Thus, the vaccination rate can be regarded as the proportion of newly acquired antibodies through vaccination. This outcome variable matches MHLW's policy goal.

### Regression Analysis

```{r reg-act}
reg_act <- main$lm(outcome_intention = FALSE)
reg_act$reg_tab(
  title = "Regressions of Behavior",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-act}
reg_act$lh_tab(
  title = "Text Message Effects on Behavior for Opt-in Incentive Group Estimated by Regressions",
  notes = " Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

As in the case of intention, the different effects of text messages for two incentive group is influenced by dimentions including age difference other than the presence or absence free vouchers. Thus, we estimate a linear probability model (\@ref(eq:regression)) and shows results in Table \@ref(tab:reg-act).

Regression analysis also shows that the Altruistic messages increase antibody test uptake only in the default incentive group. Controlling for covariates, the Altruistic messages increase antibody test uptake by a statistically significant $7.3$ pp in the default incentive group (column (2)). Furthermore, although the statistical significance is weak, the effect of this message weakens by $5.7$ pp as the cost of obtaining a free vaccination ticket becomes more expensive. As a result, the effect of the Altruistic message in the opt-in incentive group is $1.6$ pp, which is not statistically significant (column (2) in Table \@ref(tab:lh-act)). A similar trend is observed for the effect on vaccination, but it is weakly statistically significant.

We summarize the results for the other messages. Controlling for covariates, the Selfish message may have increased the antibody test-taking rate in the default incentive group, although the statistical significance is weak (column (2) in Table \@ref(tab:reg-act)). We also find that the Social Comparison message may have increased antibody testing rates in the two incentive groups (See column (2) in Table \@ref(tab:reg-act) and \@ref(tab:lh-act)). However, the effect size is larger in the default incentive group than in the opt-in incentive group (not a statistically significant difference).

As confirmed by the difference-in-means test, the Social Comparison message may increase vaccination rates in the default incentive group (column (4) in Table \@ref(tab:reg-act)). Although weakly statistically significant, the effect of this message weakens by $5.7$ pp as the cost of obtaining vaccination tickets increases. As a result, the Social Comparison message does not increase vaccination rates in the opt-in incentive group (column (4) in Table \@ref(tab:lh-act)). Again, the effect of the Altruistic message follows a similar trend.

## Monetary Value of Text Messages

Altruistic (and possibly Social Comparison) messages encourage men who received free vouchers by default to obtain antibody testing and be vaccinated. In this subsection, we attempt to evaluate the effect of these messages in the default incentive group in terms of monetary value. That is, we seek to determine the extent to which the nudge messages increase the monetary value of the rubella vaccination. In other words, we are looking for an amount of additional subsidy equivalent to the message effects in terms of government subsidies.

We use willingness to pay (WTP) for the rubella vaccine.[^other-studies] Let $WTP_i$ be an individual's willingness to pay and follow a distribution $F$. Then, for a given cost $C$, men will be vaccinated if $WTP_i \ge C$. The vaccination rate is $F_0 = 1-F(C)$. Suppose that our treated message changes WTP by $\beta$. An individual who receives a treated message will be vaccinated if $WTP_i\ge C-\beta$. The vaccination rate of the treated message group is $F_1 = 1-F(C-\beta)$. Thus, the treated message effect is $\tau = F_1-F_0=F(C)-F(C-\beta)$. From the perspective of government subsidies, the amount of subsidy equal to the effect of the nudge message $\tau$ is $\beta$. We want to estimate $\beta$.

[^other-studies]: Several studies calculate the monetary value of text messages. For example,\cite{Bursztyn2019} calculated it using the two relative effects of financial incentives and text message treatment groups. \cite{Moriwaki2020} also surveyed WTP amounts and calculated monetary value. The latter study is similar to our approach.

Once $F$, $C$, and $\tau$ are determined, we obtain $\beta $. To begin, let us discuss the estimation of $F$ (demand function). We elicit the WTP for vaccination in the first wave before participants read messages. If the vaccination costs 5,000 JPY, we ask respondents if they will get it if the local government pays $s_j$. The subsidy amounts are $s_j \in \{0, 1000, 2000, \ldots , 10000\}$. Let $s_i^{\text{min}}$ be the lowest subsidy at which respondents indicate that they would vaccinate. Let $s_i^{\text{max}}$ be the highest subsidy that respondents indicate they would not vaccinate. We can identify the willingness to pay for vaccination within the range $[5000 - s_i^{\text{max}}, 5000 - s_i^{\text{min}})$. Thus, without additional assumptions, the demand curve is step-wise, and we estimate the monetary value of the message effect with bounds.[^bound-assumption] To obtain a point estimate, we assume that the true WTP is uniformly distributed within the range $[5000 - s_i^{\text{max}}, 5000 - s_i^{\text{min}})$. Then, The vaccination demand curve can then be linearly interpolated (see Figure \@ref(fig:demand-function) in Appendix).

[^bound-assumption]: If respondents indicated that they would not vaccinate at all subsidy amounts, then $s_i^{\text{max}} = 10000$. However, we cannot define $s_i^{\text{min}}$ in the data. Therefore, we assume $s_i^{\text{min}} = 11000$. This assumption does not affect the monetary value of the messages.

In the default incentive group, eligible males receive free vaccination at no cost. Therefore, the natural setting is $C=0$. In addition, the message effect $\tau$ is used for the effect on antibody test uptake. The person taking the antibody test wants to get the antibody, i.e. the vaccination, against rubella. However, the effect of the message on vaccination is different from the effect on (true) vaccination intention, because people with a positive antibody test result cannot be vaccinated. Therefore, $\tau$ is not the effect on vaccination, but the effect on antibody testing.

In our framework, $F_0=1-F(0)$, but one potential concern remains. The message effect $\tau$ is estimated by the difference from the MHLW (control) group, and $F(0)$ does not take into account the $3.5$% antibody test uptake rate of the MHLW (control) (see Figure \@ref(fig:ttest-act-test)). Assuming that everyone who did not participate in our survey did not take the antibody test after the survey, the uptake rate of MHLW (control) can be considered as an effect of providing the message in the survey. To account for this explicitly, we use $F_0=(1-F(0))+(F(0)-F(-\alpha))$. The second term is the antibody testing rate of the control group ($3.5$%) under no vaccination cost. The demand function is estimated to be $F_0=0.7$ and $\alpha=394$.

```{r monetary-value}
value <- main$monetary_value()
value$value_table(
  title = "Estimated Monetary Value of Text Messages",
  notes = "We use the effect size of each text messages on antibody testing. Baseline is the sum of the rate of antibody test in the control and the free vaccination rates. The monetary value is the amount per person multiplied by the number of people who received the coupon in 2019 but did not use it until January 2020 ($5.29$ million). We valued it in Japanese Yen and US Dollars (1 USD = 110 JPY). The unit of monetary value per person is 1 JPY and 1 USD, respectively. The unit of total monetary value is 1 billion JPY and 1 million USD, respectively."
)
```

We find $\beta$ holding that $\tau=F(-\alpha)-F(-\beta)$. Table \@ref(tab:monetary-value) shows the estimated message value. The second and third columns show $\tau$ and $F_1=\tau+F_0$, respectively. The fourth column shows $\beta$ in terms of the value of the Japanese yen (in U.S. dollar value, shown in the sixth column). The Altruistic and Social Comparison message, which promotes antibody testing, value about 2,000 JPY (about 18 USD; 40% of assumed vaccination price) and 600 JPY (about $5.5$ USD; 12% of assumed vaccination price), respectively. The total monetary value is the product of the per capita value and the number of people who have not yet used the free vouchers issued in FY2019 ($5.29$ million as of January 2020). In the fifth column, the Altruistic and Social Comparison messages are worth 10 billion JPY (about 98 million USD) and 3 billion JPY (about 28 million USD), respectively.

# Discussion and Conclusions {#conclusion}

This study uses RCTs to investigate effective messages for promoting rubella antibody testing and vaccination in two situations regarding financial incentives. Our experiment reveals that the Altruistic message, which emphasizes the negative externality of infection, increases the intention for antibody testing uptake by $14.3$ pp among men who already received free vaccination tickets in FY2019. However, this message is less effective for men who incur transaction costs to obtain the vaccination tickets. There may be a statistically significant difference in the effect of this message between the two groups.

Similar results are found for the antibody test uptake. Among men who had already received vaccination vouchers in FY 2019, the Altruistic message increases the antibody test uptake by $7.5$ pp, which is equivalent to a subsidy of 40% of the vaccination price. However, this message is less effective for men who incurred the cost of obtaining the vaccination tickets. The effect between the two groups may be statistically significant.

This finding suggests that text message reminders are effective when financial incentives and reminders are closely combined. In addition to the Altruistic message, the Selfish and the Social Comparison message may also raise the intention and the acutual uptake rate for the antibody testing among men who already received the vaccination tickets by default. However, these effect sizes are not large enough to maintain statistical power, requiring a re-examination with a large sample size.

One potential concern is that all behavior-related outcomes were self-reported. These outcomes may contain recall bias. We believe that these biases are less problematic because Wave 2 measures behavior within the last month (the time of Wave 1). The self-reported behavioral outcomes may also be subject to the experimenter demand effect and social desirability bias. To address these biases, our regression analysis directly controls for respondents' psychological factors related to these biases (e.g., following social norm). Even if these biases cannot be eliminated perfectly, they are not fatal to the identification of message effects since this study is a RCT and if these biased exist to the same extent in each group. 

Finally, we discuss three points about mechanisms. The first is the mechanism of the Altruistic messages. The effect of Altruistic message (especially on the intention to test for antibodies) is due to a change in the content of the message rather than to the addition of a simple expression of age. The Altruistic message emphasizes the possibility of disability in infants and appeals to the negative externalities of not vaccinating. We analyze the heterogeneity of the message content effect to test which individuals respond more strongly to this message content.

First, in Wave 1, we examine the knowledge that infants born to infected pregnant women may have disabilities and test the heterogeneity of the effect of the altruistic message content on antibody testing intentions depending on whether respondents possessed this knowledge (see column (1) of Table \@ref(tab:reg-mechanism) in the Appendix). The results show that the effect of the altruistic message content may be more effective for those who do not possess the knowledge than for those who do. Although there are no statistically significant difference between the effects with and without knowledge, the effects of message content for those with knowledge are not statistically significant. Thus, altruistic message content may modify knowledge about the negative externalities of infection.

It is also important whether a man is altruistic, caring about others' benefit (externality). We investigate whether he feels pleasure in actions for others on a 5 scale in Wave 1 and test the heterogeneous effect of the Altruistic message content by the extent to which he does (see column (2) of Table \@ref(tab:reg-mechanism) in the Appendix). The results show that the more altruistic one is, the stronger the effect of the Altruistic message content (this trend is statistically significant). Thus, the Altruistic messages may not be effective for those who do not care about others, even if they perceive negative externalities from reading messages.

The second argument is the effect on vaccination rates. Our experiments reveal that the Altruism and the Social Comparison messages may increase vaccination rates among men who received free vaccination tickets by default. The message effect on vaccination is created through two channels. First, the messages increase the number of negative individuals who need to be vaccinated. Second, the messages encourage unvaccinated negative individuals to vaccinate. Our data suggest that the first channel is more important than the second.

Table \@ref(tab:summary-behavior-default) in the Appendix shows the number of men who had antibody testing, who had a negative antibody test, and who were vaccinated in each experimental arm in the default incentive group. This table shows that most of those with negative antibody test results were vaccinated in all experimental arms. Furthermore, the number of negative antibody tests varied between experimental arms. Especially, the 25% ($=1/4$) antibody tests are negative in the MHLW (Control) message group. In contrast, the negative ratios of antibody tests for the Altruistic and Social Comparison messages, which may have a positive effect on vaccination, are 50% ($=7/14$) and 56% ($=5/9$), respectively.[^negative-selfish] Thus, the experimental arms with higher vaccination rates have a greater negative ratio, resulting in a positive effect on vaccination. However, the difference in the ratio of negative antibody tests is not statistically significant.

[^negative-selfish]: The negative ratio of antibody testing for the Selfish message, which is only effective for antibody test uptake, is 30% ($=3/10$). This value is similar to the MHLW (control) message.

A final discussion is why text messages are ineffective in groups that must incur transaction costs to obtain the free vaccination tickets. Our messages may not increase the value of antibody testing and vaccination sufficiently to outweigh their cost. In addition, another possibility is low awareness of rubella immunization campaign beginning in FY2019. Before presenting the messages, we inquire about the MHLW's policy in Wave 1. As a result, approximately 77.5% are unaware of the vaccination campaign Thus, even if they read the messages and realized the importance of rubella antibody testing and vaccination, they would believe they had to pay for these preventive actions.[^strategic-behavior]

[^strategic-behavior]: The fact that many people are unaware of the additional routine rubella vaccinations precludes the possibility that they stopped getting antibody testing and were vaccinated in the first year (FY2019) because they expected to automatically receive the voucher the following year.

The last two arguments are important issues outside our context. The second argument concerns the targeting of interventions [e.g., @Finkelstein2019]. That is, the question is whether marginal individuals whose behavior is changed by a policy intervention receive significant benefits from that policy. In our context, we suggest that the Altruistic message increases the number of negative individuals who receive a large benefit (vaccination) from the FY2019 vaccination campaign. The third argument relates to testing the effectiveness of vouchers [e.g., @Kacker2022]. The experimental data in this study alone do not allow us to fully explore these arguments, and they are a topic for future research.

\clearpage
# (APPENDIX) Appendix {-}
# Tables and Figures

```{r covariate-list}
setup$summary_control(here("assets/vars_descript.csv"))
```

```{r balance-int-default}
main$balance_control(
  title = "Balance Tests for Default Incentive Groups (Sample for Estimating Effect on Intention)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2--8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r balance-int-optin}
main$balance_control(
  default_voucher = FALSE,
  title = "Balance Tests for Opt-In Incentive Group (Sample for Estimating Effect on Intention)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2--8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r reg-int-woA}
reg_woA <- main$lm(exclude_A = TRUE)
reg_woA$reg_tab(
  title = "Massage Content Effects on Intentions Compared to MHLW (Age)",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-int-woA}
reg_woA$lh_tab(
  title = "Message Content Effects for Opt-in Incentive Group Estimated by Regressions",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

```{r balance-act-default}
main$balance_control(
  outcome_intention = FALSE,
  title = "Balance Tests for Default Incentive Group (Sample for Estimating Effect on Behavior)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2--8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r balance-act-optin}
main$balance_control(
  outcome_intention = FALSE,
  default_voucher = FALSE,
  title = "Balance Tests for Opt-in Incentive Group (Sample for Estimating Effect on Behavior)",
  notes = "Notes: Table \\\\ref{tab:covariate-list} describles variables. Columns 2--8 show sample averages for each experimental arm. Column 9 shows p-value of the joint null hypothesis (F-test)."
)
```

```{r reg-act-woA}
reg_act_woA <- main$lm(outcome_intention = FALSE, exclude_A = TRUE)
reg_act_woA$reg_tab(
  title = "Message Content Effects on Behaivor Compared to MHLW (Age)",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r lh-act-woA}
reg_act_woA$lh_tab(
  title = "Message Content Effects for Opt-in Incentive Group Estimated by Regressions",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control). The reference group is MHLW (Age). Message effects are estimated by a sum of main term of treatment dummy and cross term between treatment dummy and opt-in dummy."
)
```

```{r demand-function, fig.cap = "Demand Curve of Rubella Vaccination for Default Incentive Group. Notes: Black triangles indicate the baseline vaccination rate $F_0$ and the corresponding WTP."}
value$demand_curve()
```

```{r reg-mechanism}
mechanism <- main$lm_mechanism()
mechanism$reg_tab(
  title = "Heterogeneous Effects of Altruistic Message Contents",
  notes = "Notes: * $p < 0.1$; ** $p < 0.05$; *** $p < 0.01$. Robust standard errors are in parentheses. We exclude from the sample those assigned to MHLW (control), The reference group is MHLW (Age). Covariate ``Other nudges'' is a dummy that indicating respondents are assigned to the Selfish, Social Comparison, Deadline, and Covenient message group. Covariate ``Handicap'' is a dummy that respondent knows that infants born to infected pregnant women may have disabilities. Covariates ``Generosity'' indicates on a 5-point scale the degree to which respondent feels pleasure in actionts for others. Respondents who give a score of 5 to this are the most generous. Covariates are age, education year, annual income, usual health behavior (exercise, medical checkup and ful shot habit) and preference for compliance with social norm."
)
```

```{r summary-behavior-default}
main$summary_behavior(
  title = "Number of Anitbody Testing, Negatives, and Vaccinations in Default Incentive Group"
)
```